# Load libraries

Note that I've loaded relevant libraries and create a merged dataframe of all Pavlovia responses and Qualtrics data.

```{r, include = FALSE}
library(tidyverse)
library(purrr)

# Load in data
library(fs)

# Plotting
library(plotly)
library(wesanderson)

# Statistical Analysis
library(psych)
library(lme4)
library(lmerTest)
library(r2mlm)
library(rockchalk)
library(rstatix)
```

```{r read in data, include = FALSE}
# Function to read and process individual group data
read_and_label <- function(data_path, label) {
  list_csv <- dir_ls(data_path, regexp = "\\.csv$")
  map_dfr(list_csv, read_csv, .id = "file") %>%
    mutate(
      participant = str_replace(file, "^.*?/(.*?)\\.csv$", "\\1"),
      ctl_or_exper = label
    )
}

# Read and label experimental data
data_exper <- read_and_label("/Users/christinahuber/Desktop/ldt-replication/data", "exper")

# Read and label control data
data_ctl <- read_and_label("/Users/christinahuber/Desktop/ldt_no_images/data", "ctl")

# Combine the data
data <- bind_rows(data_exper, data_ctl)
```

```{r process data, include = FALSE}
# Process the combined data
data_processed <- data %>%
  # Remove rows without values in "on_time.keys" or "on_time_2.keys"
  filter(!is.na(on_time.keys) & !is.na(on_time_2.keys)) %>%
  # Remove brackets and quotation marks from relevant columns
  mutate(across(everything(), ~str_replace_all(., "[\\[\\]\"]", ""))) %>%
  # Create "good_on_left" column and choices
  mutate(
    good_on_left = as.numeric(as.logical(as.integer(str_sub(participant, -1)) %% 2)),
    choice_1 = case_when(
      good_on_left == 1 & on_time.keys == "a" ~ 1,
      good_on_left == 1 & on_time.keys == "l" ~ 0,
      good_on_left == 0 & on_time.keys == "a" ~ 0,
      good_on_left == 0 & on_time.keys == "l" ~ 1,
      TRUE ~ NA_real_
    ),
    choice_2 = case_when(
      good_on_left == 1 & on_time_2.keys == "a" ~ 1,
      good_on_left == 1 & on_time_2.keys == "l" ~ 0,
      good_on_left == 0 & on_time_2.keys == "a" ~ 0,
      good_on_left == 0 & on_time_2.keys == "l" ~ 1,
      TRUE ~ NA_real_
    )
  ) %>%
  # Convert reaction time data to numeric
  mutate(
    on_time.rt = as.numeric(on_time.rt),
    on_time_2.rt = as.numeric(on_time_2.rt)
  )
```


```{r filter columns, include = FALSE}
# Read in the "qualtrics.csv" file
qualtrics <- read.csv("qualtrics.csv")

# Calculate the number of incorrect attention check responses and the total responses
attention_check_summary <- data_processed %>%
  summarize(
    total_responses = n(),
    incorrect_Woo1_15 = sum(Woo1_15 != 1, na.rm = TRUE),
    incorrect_Woo3_6 = sum(Woo3_6 != 4, na.rm = TRUE),
    correct_attention_checks = sum(Woo1_15 == 1 & Woo3_6 == 4, na.rm = TRUE)
  )

# Print the summary
print(attention_check_summary)

# ------------------------------
# 1. Data transformation and filtering
# ------------------------------

filtered_columns <- data_processed %>%
  select(
    participant, base_image, base_word, target_word, target_condition,
    on_time.rt, on_time_2.rt, choice_1, choice_2, correct_answer_1,
    correct_answer_2, run_num, early_keys.keys,
    matches("^(Woo[123]_|NR[12]_|AOT_)") # grab individual difference variables
  ) %>%
  filter(
    Woo1_15 == 1, Woo3_6 == 4, is.na(early_keys.keys),
    !is.na(on_time_2.rt), !is.na(on_time.rt),
    on_time.rt >= 0.2, on_time.rt <= 1.5,
    on_time_2.rt >= 0.2, on_time_2.rt <= 1.5
  ) %>%
  mutate(
    target_condition = factor(target_condition, levels = c("DI", "II", "NI", "CI", "DD", "ID", "ND", "CD", "DN", "IN", "NN", "CN", "DC", "IC", "NC", "CC")),
    participant = as.numeric(participant),
    across(c(starts_with("NR1_"), starts_with("NR2_"), starts_with("AOT_"), starts_with("Woo1_"), starts_with("Woo2_"), starts_with("Woo3_")), as.numeric),
    condition = target_condition
  ) %>%
  separate(target_condition, into = c("code1", "code2"), sep = 1) %>%
  group_by(code1) %>%
  mutate(first_RT_mean = mean(on_time.rt)) %>%
  ungroup() %>%
  mutate(
    base_image = gsub("[^0-9]", "", base_image),
    first_choice_wrong = ifelse(choice_1 != correct_answer_1, 1, 0),
    second_choice_wrong = ifelse(choice_2 != correct_answer_2, 1, 0),
    difference_rt = on_time_2.rt - on_time.rt
  ) %>%
  filter(choice_1 == correct_answer_1 & choice_2 == correct_answer_2)

# ------------------------------
# 2. Additional data manipulations
# ------------------------------

# Marcel type
filtered_columns <- filtered_columns %>%
  mutate(marcel_type = case_when(
    code1 == code2 ~ "congruent",
    code2 == "I" ~ "control",
    TRUE ~ "incongruent"
  ))

# Stephanie NR composite
filtered_columns <- filtered_columns %>%
  mutate(
    NR2_1_reverse = 8 - NR2_1,
    NR2_3_reverse = 8 - NR2_3,
    Stephanie_NR_composite = NR2_1_reverse + NR2_2 + NR2_3_reverse + NR2_4
  )

# Christina NR composite
filtered_columns <- filtered_columns %>%
  mutate(
    NR1_2_reverse = 8 - NR1_2,
    NR1_3_reverse = 8 - NR1_3,
    NR1_5_reverse = 8 - NR1_5,
    Christina_NR_composite = NR1_1 + NR1_2_reverse + NR1_3_reverse + NR1_4 + NR1_5_reverse + NR1_6
  )

# Reverse coding for certain columns
reverse_columns <- c("Woo1_1", "Woo1_2", "Woo1_3", "Woo1_4", "Woo1_5", "Woo1_6", "Woo1_7", "Woo1_8", "Woo1_9", "Woo1_10", "Woo1_11", "Woo1_12", "Woo1_13", "Woo1_14", "Woo1_16", "Woo1_17", "Woo1_18", "Woo1_19", "Woo2_5", "Woo2_6", "Woo2_7", "Woo2_8", "Woo2_9", "Woo2_10", "Woo2_12")

for (col in reverse_columns) {
  filtered_columns[filtered_columns[col] != "NA", col] <- 5 - filtered_columns[filtered_columns[col] != "NA", col]
}

# ------------------------------
# 3. Create a dataframe for facets
# ------------------------------

# List for each facet
facets <- list(
  Intellectual_Efficiency = c('Woo1_6', 'Woo1_8', 'Woo1_13', 'Woo2_4', 'Woo2_7', 'Woo2_15', 'Woo3_4', 'Woo3_9', 'Woo3_16'),
  Ingenuity = c('Woo1_4', 'Woo1_10', 'Woo1_14', 'Woo2_1', 'Woo2_9', 'Woo2_16', 'Woo3_7', 'Woo3_10', 'Woo3_19'),
  Curiosity = c('Woo1_2', 'Woo1_9', 'Woo1_17', 'Woo2_5', 'Woo2_12', 'Woo2_17', 'Woo3_3', 'Woo3_11', 'Woo3_17'),
  Aesthetics = c('Woo1_3', 'Woo1_7', 'Woo1_16', 'Woo2_2', 'Woo2_8', 'Woo2_14', 'Woo3_5', 'Woo3_12', 'Woo3_18'),
  Tolerance = c('Woo1_5', 'Woo1_12', 'Woo1_18', 'Woo2_3', 'Woo2_11', 'Woo2_18', 'Woo3_2', 'Woo3_13', 'Woo3_15'),
  Depth = c('Woo1_1', 'Woo1_11', 'Woo1_19', 'Woo2_6', 'Woo2_10', 'Woo2_13', 'Woo3_1', 'Woo3_8', 'Woo3_14')
)

facet_df <- do.call(rbind, lapply(names(facets), function(facet) {
  data.frame(Facet = facet, t(facets[[facet]]))
}))

colnames(facet_df) <- c("Facet", "Woo1", "Woo2", "Woo3", "Woo4", "Woo5", "Woo6", "Woo7", "Woo8", "Woo9")
print(facet_df)

# List of facets with their respective items
facets_list <- list(
  intellectual_efficiency = intellectual_efficiency,
  ingenuity = ingenuity,
  curiosity = curiosity,
  aesthetics = aesthetics,
  tolerance = tolerance,
  depth = depth
)

# Compute composite scores for each facet
filtered_columns <- filtered_columns %>%
  mutate(across(
    all_of(names(facets_list)),
    ~rowSums(select(., facets_list[[.]]), na.rm = TRUE),
    .names = "composite_{.}"
  ))

filtered_columns <- filtered_columns %>%
  mutate(
    correct_answer_1 = if_else(correct_answer_1 == "yes", 1, 0),
    correct_answer_2 = if_else(correct_answer_2 == "yes", 1, 0)
  )
```

```{r second choice wrong df, include = FALSE}
mistakes_included <- filtered_columns

second_choice_wrong <- filtered_columns %>% 
  filter(choice_2 != correct_answer_2 & choice_1 == correct_answer_1)

df <- second_choice_wrong$condition %>%
  table() %>%
  as.data.frame() %>%
  arrange(Var1)
```

```{r means table, include = FALSE}
means <- filtered_columns %>%
  dplyr::group_by(condition) %>%
  dplyr::summarize(on_time_rt_mean = mean(as.numeric(on_time.rt)),
                   on_time_2_rt_mean = mean(as.numeric(on_time_2.rt)),
                   first_RT_mean = mean(first_RT_mean),
                   difference_mean = mean(as.numeric(difference_rt)))

# Melt the means dataframe to long format
means_long <- reshape2::melt(means, id.vars = "condition")
```

```{r 2x3 df, include = FALSE}
two_by_three <- filtered_columns %>%
  filter(code1 %in% c("D", "N")) %>%
  mutate(
    code1 = factor(code1),
    code2 = factor(code2)
  ) %>%
  group_by(code1, code2) %>%
  summarise(mean_rt = mean(on_time_2.rt, na.rm = TRUE)) %>%
  mutate(rt_gm = exp(mean(log(on_time_2.rt, na.rm = TRUE))))  # if you need geometric mean

```

```{r}
# Define a function to filter, group, and count
pick_cols_and_count <- function(data, code1_vals, code2_vals) {
  data %>%
    filter(code1 %in% code1_vals, code2 %in% code2_vals) %>%
    group_by(participant, code2, ctl_or_exper) %>%
    dplyr::count(second_choice_wrong) %>%
    pivot_wider(names_from = "second_choice_wrong", values_from = c("n"), values_fill = 0) %>%
    pivot_wider(names_from = "code2", values_from = c("0", "1"))
}

# Define a function to filter, group, and calculate means
calculate_means <- function(data, code1_vals, code2_vals) {
  data %>%
    filter(code1 %in% code1_vals, code2 %in% code2_vals) %>%
    mutate(across(c(code1, code2), as.factor)) %>%
    mutate(code1 = relevel(code1, ref = "N"), code2 = relevel(code2, ref = "D")) %>%
    group_by(code1, ctl_or_exper) %>%
    summarise(mean_RT = mean(on_time_2.rt))
}

# Use the functions for different conditions
DN_vs_DI <- pick_cols_and_count(filtered_columns, c("D"), c("N", "I"))
ND_vs_NI <- pick_cols_and_count(filtered_columns, c("N"), c("D", "I"))
DD_vs_NN <- pick_cols_and_count(filtered_columns, c("D", "N"), c("D", "N"))
DN_vs_ND <- pick_cols_and_count(filtered_columns, c("D", "N"), c("N", "D"))

DI_vs_DN_means <- calculate_means(filtered_columns, c("D"), c("N", "I"))
NI_vs_ND_means <- calculate_means(filtered_columns, c("N"), c("D", "I"))
DN_vs_ND_means <- calculate_means(filtered_columns, c("D", "N"), c("N", "D"))
```


```{r calculate and print proportions, include = FALSE}
# Function to calculate incorrect proportions and differences
calculate_proportions <- function(df, incorrect_suffix, correct_suffix) {
  df %>%
    group_by(participant, ctl_or_exper) %>%
    mutate(
      I_prop_incorrect = case_when(
        .data[[paste0("1", incorrect_suffix)]] >= 1 ~ 
          .data[[paste0("1", incorrect_suffix)]] / 
          (.data[[paste0("1", incorrect_suffix)]] + .data[[paste0("0", incorrect_suffix)]])
        ,
        TRUE ~ 0
      ),
      X_prop_incorrect = case_when(
        .data[[paste0("1", correct_suffix)]] >= 1 ~ 
          .data[[paste0("1", correct_suffix)]] / 
          (.data[[paste0("1", correct_suffix)]] + .data[[paste0("0", correct_suffix)]])
        ,
        TRUE ~ 0
      ),
      difference = X_prop_incorrect - I_prop_incorrect
    ) %>%
    ungroup()
}

# Apply the function to both data frames
reshape <- calculate_proportions(reshape, "_I", "_N")
reshape2 <- calculate_proportions(reshape2, "_I", "_D")

# Merge NR_df with both reshape and reshape2
reshape <- merge(reshape, NR_df, by = "participant")
reshape2 <- merge(reshape2, NR_df, by = "participant")

# Summarize the mean incorrect proportions for DN vs DI and ND vs NI
sum1 <- reshape %>%
  summarise(DN = mean(N_prop_incorrect),
            DI = mean(I_prop_incorrect))

sum2 <- reshape2 %>%
  summarise(ND = mean(X_prop_incorrect),
            NI = mean(I_prop_incorrect))

# Combine sum1 and sum2 into a single data frame
sum_combined <- bind_rows(sum1, sum2)

# Transpose dataframe and convert to 1-column dataframe
sum_new <- as.data.frame(t(sum_combined))

# Add row names as a column called "condition"
sum_new <- rownames_to_column(sum_new, var = "condition")

# View the resulting dataframe
sum_new

```

```{r summarize conditions, include = FALSE}
# merge the two data frames
merged_df <- merge(two_by_three, reshape, by = "participant", all = TRUE)

# relevel factors and summarize data in one chain
summary_df <- merged_df %>%
  mutate(across(c(code1, code2), factor, levels = c("N", "I"))) %>%
  group_by(code1, code2, ctl_or_exper) %>%
  summarise(mean_rt = mean(on_time_2.rt, na.rm = TRUE),
            se_rt = sd(on_time_2.rt, na.rm = TRUE) / sqrt(n()), .groups = 'drop')

summary_df
```

```{r}
# If you want to check the correlation between Woo_composite and difference_rt for incongruent trials:
incongruent_data <- filtered_columns %>%
  filter(marcel_type == "incongruent")
```




# Exploratory data analysis

```{r, echo = FALSE}
# count number of distinct participants
num_participants <- length(unique(data$participant))

# print result
cat("Number of participants:", num_participants)
```

```{r}
# Create the scatter plot
ggplot(filtered_columns, aes(x = on_time.rt, y = on_time_2.rt, color = condition)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Response to Word 1", y = "Response to Word 2") +
  theme_minimal()

cor.test(filtered_columns$on_time.rt, filtered_columns$on_time_2.rt)
```

First, I want to gain a sense of the distribution of responses to both the priming word (histogram 1) and target word (histogram 2.)

```{r, echo = FALSE}
# Histogram of on_time.keys (reaction time to first word)
ggplot(filtered_columns, aes(x = on_time.rt)) +
  geom_histogram(binwidth = 0.01) +
  labs(
    title = "Distribution for first key press (without cutoffs)", 
    x = "RTs", 
    y = "Frequency")

# Histogram of on_time_2.keys (reaction time to second word)
ggplot(filtered_columns, aes(x = on_time_2.rt)) +
  geom_histogram(binwidth = 0.01) +
  labs(
    title = "Distribution for second key press (without cutoffs)", 
    x = "RTs", 
    y = "Frequency")

# Histogram of on_time.keys (reaction time to first word)
ggplot(filtered_columns, aes(x = on_time.rt)) +
  geom_histogram(binwidth = 0.01) +
  labs(
    title = "Distribution for first key press (without cutoffs)", 
    x = "RTs", 
    y = "Frequency")

# Histogram of on_time_2.keys (reaction time to second word)
ggplot(filtered_columns, aes(x = on_time_2.rt)) +
  geom_histogram(binwidth = 0.01) +
  labs(
    title = "Distribution for second key press (without cutoffs)", 
    x = "RTs", 
    y = "Frequency")


```

The data have a slight skew, although transforming them could remove variance of interest.

Now, let's take a look at the means by condition, bearing in mind that trials ending in "I" are slowed down about 30msec due to "yes" bias -- i.e., participants are slower to respond "no" to irrelevant words than they are to respond "yes" to relevant words.

```{r, echo = FALSE}
print(means)
```

```{r}
new_order <- c("DD", "ID", "ND", "DI", "II", "NI", "DN", "IN", "NN")
my_order <- c("DD", "DI", "DN", "ID", "II", "IN", "ND", "NI", "NN")

filtered_columns$condition <- factor(filtered_columns$condition, levels = my_order)
label_df <- label_df %>% filter(condition %in% my_order)
```

## Trait individual differences

Now, let's take a look at the distribution of participants' trait naive realism scores.

```{r NR plots, echo = FALSE, warning = FALSE}
ggplot(filtered_columns, aes(x = Stephanie_NR_composite)) +
  labs(title = "Distribution of NR composite scores", x = "RTs", y = "Frequency") +
  geom_histogram(fill="#69b3a2", color="#e9ecef") +
  facet_wrap(~ctl_or_exper)

ggplot(filtered_columns, aes(x = Christina_NR_composite)) +
  labs(title = "Distribution of NR composite scores", x = "RTs", y = "Frequency") +
  geom_histogram(fill="#69b3a2", color="#e9ecef") +
  facet_wrap(~ctl_or_exper)

```

```{r NR correlations}
compute_correlation <- function(df, composite_col) {
  result <- cor.test(df[[composite_col]], df$difference_rt)
  return(list(correlation = result$estimate, p.value = result$p.value))
}

results_filtered <- compute_correlation(filtered_columns, "Stephanie_NR_composite")
results_incongruent <- compute_correlation(incongruent_data, "Stephanie_NR_composite")

cat("For filtered_columns:\nCorrelation between difference_rt and Stephanie_NR_composite:", results_filtered$correlation, "\nP-value:", results_filtered$p.value, "\n\n")
cat("For incongruent_data:\nCorrelation between difference_rt and Stephanie_NR_composite:", results_incongruent$correlation, "\nP-value:", results_incongruent$p.value)
```


```{r woo plots, echo = FALSE, warning = FALSE}
# Create a Woo_composite variable by averaging all the Woo columns
filtered_columns <- filtered_columns %>%
  mutate(Woo_composite = rowMeans(select(., starts_with("Woo"))))

ggplot(filtered_columns, aes(x = Woo_composite)) +
  labs(title = "Distribution of NR composite scores", x = "RTs", y = "Frequency") +
  geom_histogram(fill="#69b3a2", color="#e9ecef") +
  facet_wrap(~ctl_or_exper)

cor_test <- cor.test(incongruent_data$Woo_composite, incongruent_data$difference_rt)

print(cor_test)

ggplot(filtered_columns, aes(x = Woo_composite)) +
  labs(title = "Distribution of Woo openness composite scores", x = "RTs", y = "Frequency") +
  geom_histogram(fill="#69b3a2", color="#e9ecef") +
  facet_wrap(~ctl_or_exper)

# Creating composite columns for each facet
filtered_columns <- filtered_columns %>%
  mutate(
    Intellectual_Efficiency_composite = rowMeans(select(., intellectual_efficiency)),
    Ingenuity_composite = rowMeans(select(., ingenuity)),
    Curiosity_composite = rowMeans(select(., curiosity)),
    Aesthetics_composite = rowMeans(select(., aesthetics)),
    Tolerance_composite = rowMeans(select(., tolerance)),
    Depth_composite = rowMeans(select(., depth))
  )

# List of composite names
composite_names <- c(
  "Intellectual_Efficiency_composite", 
  "Ingenuity_composite", 
  "Curiosity_composite", 
  "Aesthetics_composite", 
  "Tolerance_composite", 
  "Depth_composite")

# Loop over each composite and produce a histogram
for (composite in composite_names) {
  
  p <- ggplot(filtered_columns, aes_string(x = composite)) +
    labs(title = paste("Distribution of", composite, "scores"), x = "Composite Score", y = "Frequency") +
    geom_histogram(fill="#69b3a2", color="#e9ecef") +
    facet_wrap(~ctl_or_exper)
  
  print(p)
}
```

```{r woo correlations, include = FALSE}
# Compute correlations and p-values
results <- lapply(composite_names, function(col_name) {
  test <- cor.test(incongruent_data[[col_name]], incongruent_data$difference_rt)
  return(list(correlation = test$estimate, p.value = test$p.value))
})

# Extract p-values
p_values <- sapply(results, function(res) res$p.value)

# Correct for multiple comparisons
adjusted_p_values <- p.adjust(p_values, method = "holm")

# Combine results into a dataframe
correlation_df <- data.frame(
  Facet = composite_names,
  Correlation = sapply(results, function(res) res$correlation),
  PValue = p_values,
  AdjustedPValue = adjusted_p_values
)

print(correlation_df)
```


## RTs

Here are three visualizations of the reaction times. Difference scores compare responses to the priming word vs. target word. The conditions of interest are the first and last three sets of columns.

```{r, echo = FALSE}
means_long %>%
  mutate(condition = factor(condition, levels = my_order)) %>%
  filter(variable %in% c("on_time_rt_mean", "on_time_2_rt_mean"), condition %in% my_order) %>%
  ggplot(aes(x = condition, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = wes_palette("Darjeeling2")) +
  labs(x = "Target Condition", y = "Mean On-Time RT", fill = "") +
  theme_minimal() +
  facet_wrap(~ctl_or_exper)
```

# Pairwise comparisons

```{r, echo = FALSE}
# Combine datasets and add a 'condition_comparison' column to identify each set
combined_conditions <- bind_rows(
  DN_vs_DI %>% mutate(condition_comparison = "DN_vs_DI"),
  ND_vs_NI %>% mutate(condition_comparison = "ND_vs_NI"),
  DD_vs_NN %>% mutate(condition_comparison = "DD_vs_NN"),
  DN_vs_ND %>% mutate(condition_comparison = "DN_vs_ND")
)

# Perform pairwise t-tests
t_test_results <- combined_conditions %>%
  split(.$condition_comparison) %>%
  map(~pairwise.t.test(.$measure, .$participant, p.adjust.method = "bonferroni"))

# Print the t-test results
print(t_test_results)

color_palette <- brewer.pal(4, "Pastel1")

# Plotting combined data with the chosen color palette
combined_conditions %>%
  ggplot(aes(x = participant, y = measure, fill = condition_comparison)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~condition_comparison) + # separate panels for each condition comparison
  scale_fill_manual(values = color_palette) +
  labs(x = "Participant", y = "Measure", fill = "Condition Comparison") +
  theme_minimal()  +
  facet_wrap(~ctl_or_exper)

```

# 2x3 interaction

## Dummy coding

```{r dummy coded model, echo = FALSE}
# Adjusted custom label function
add_custom_labels <- function(df) {
  df %>%
    mutate(marcel_type = case_when(
      str_detect(condition, "I$") ~ "control",
      str_detect(condition, "DD$") | str_detect(condition, "NN$") ~ "congruent",
      str_detect(condition, "DN$") | str_detect(condition, "ND$") ~ "incongruent",
      TRUE ~ as.character(condition)
    ))
}

# Apply custom labels
two_by_three <- add_custom_labels(two_by_three)

two_by_two <- two_by_three %>%
  filter(marcel_type %in% c("incongruent", "control"))

# Adjusted function to fit LMER model and print summary
fit_and_summarize <- function(df, fixed_effects, random_effects = "(1 | participant)", data_name = "Data") {
  model <- lmer(paste("on_time_2.rt ~", fixed_effects, random_effects), data = df, REML = TRUE)
  cat("\nSummary for", data_name, ":\n")
  print(summary(model))
  return(model)  # Return for possible further use
}

# Fit models and display summaries using the new marcel_type column
fit_and_summarize(two_by_two, "code1 * marcel_type * ctl_or_exper", data_name = "Two-by-Two")
fit_and_summarize(subset(two_by_two, code1 == "N"), "marcel_type * ctl_or_exper", data_name = "N Only")
fit_and_summarize(subset(two_by_two, code1 == "D"), "marcel_type * ctl_or_exper", data_name = "D Only")

# Relevel factors in two_by_three
two_by_three <- two_by_three %>%
  mutate(code1 = relevel(code1, ref = "N"),
         code2 = relevel(code2, ref = "I"),
         run_num = factor(run_num),
         run_num = relevel(run_num, ref = "1"))  # Assuming '1' should be the reference level

# Fit model for two_by_three including run_num using the new marcel_type column
fit_and_summarize(two_by_three, "code1 * marcel_type * ctl_or_exper", data_name = "Two-by-Three")
```

## Simple coding

```{r}
########### custom coding ################

# Print current levels of the factor variables
print(levels(two_by_three$code1))
print(levels(two_by_three$marcel_type))

# Assign contrasts based on the order of the levels printed
contrasts(two_by_three$code1) <- c(1, -1)  # Make sure this matches the desired contrast for the levels of code1
contrasts(two_by_three$marcel_type) <- c(1, 0, -1)  # Make sure this matches the desired contrast for the levels of marcel_type

# Now you can fit the model knowing that the contrasts correspond to the factor levels correctly
marcel_model <- lmer(on_time_2.rt ~ code1 * marcel_type * ctl_or_exper + (1 | participant), data = two_by_three, REML = TRUE)
summary(marcel_model)

# Now you can fit the model knowing that the contrasts correspond to the factor levels correctly
marcel_model_NR <- lmer(
  on_time_2.rt ~ code1 * marcel_type * Christina_NR_composite * ctl_or_exper + (1 | participant), 
  data = two_by_three, 
  REML = TRUE)

summary(marcel_model_NR)

marcel_model_Woo <- lmer(
  on_time_2.rt ~ code1 * marcel_type * Woo_composite * ctl_or_exper + (1 | participant), 
  data = two_by_three, 
  REML = TRUE)

summary(marcel_model_Woo)

```

# Interaction visualization

```{r, echo = FALSE}
# Reorder the levels of the factor variables
two_by_three$code1 <- factor(two_by_three$code1, levels = c("D", "N"))
two_by_three$code2 <- factor(two_by_three$code2, levels = c("D", "I", "N"))

summary_df <- plyr::ddply(two_by_three, c("code1", "code2", "ctl_or_exper"),
                          summarize, mean_rt = mean(on_time_2.rt),
                          se_rt = sd(on_time_2.rt) / sqrt(length(on_time_2.rt)))

summary_df <-summary_df %>% filter(code2 %in% c("D", "I", "N"))

# Add a new column with custom labels
summary_df$custom_labels <- c("congruent", "control", "incongruent", "incongruent", "control", "congruent")

```


```{r}
# Plot the data with error bars
plot2a <- ggplot(summary_df, aes(x = code1, y = mean_rt, fill = code2)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(
    aes(ymin = mean_rt - se_rt,
        ymax = mean_rt + se_rt),
    width = 0.2,
    position = position_dodge(0.9)) +
  labs(
    x = "First Word", 
    y = "Reaction time (sec)") +
  scale_fill_manual(
    name = "Second Word", 
    labels = c("Dominant", "Irrelevant", "Nondominant"),
    values = wes_palette("GrandBudapest1")) +
  theme_minimal() +
  scale_x_discrete(labels = c("Dominant", "Nondominant")) +
  coord_cartesian(ylim = c(.2, .8)) +
  facet_wrap(~ctl_or_exper)

plot2a
```


```{r}
# Add the new column based on conditions
two_by_three <- two_by_three %>%
  mutate(congruency = case_when(
    as.character(code1) == as.character(code2) ~ "congruent",
    code2 == "I" ~ "control",
    TRUE ~ "incongruent"
  ))


# Summarize mean_rt and se_rt based on the new column
summary_by_congruency <- two_by_three %>%
  group_by(congruency, ctl_or_exper) %>%
  summarize(
    mean_rt = mean(on_time_2.rt),
    se_rt = sd(on_time_2.rt) / sqrt(n())
  )

```

```{r exper only anova}
exper_only <- two_by_three %>% filter(ctl_or_exper == "exper")

anova_result <- aov(on_time_2.rt ~ congruency, data = exper_only)
summary(anova_result)

library(emmeans)
pairwise_comparisons <- emmeans(anova_result, pairwise ~ congruency, adjust = "tukey")
pairwise_comparisons

# Convert congruency to a factor
exper_only$congruency <- as.factor(exper_only$congruency)

# Set "control" as the reference level
exper_only$congruency <- relevel(exper_only$congruency, ref = "control")

# Now fit the linear regression model
model <- lm(on_time_2.rt ~ congruency, data = exper_only)
summary(model)
```


```{r}
plot1 <- ggplot(summary_by_congruency, aes(x = congruency, fill = congruency, y = mean_rt)) +
  geom_bar(stat = "identity", width = 0.7) +
  geom_errorbar(
    aes(ymin = mean_rt - se_rt, 
        ymax = mean_rt + se_rt),
    width = 0.2) +
  labs(
    x = "Word type", 
    y = "Reaction time (sec)") +
  theme_light() +
  coord_cartesian(ylim = c(.2, .8)) +
  scale_fill_manual(
    values = wes_palette("GrandBudapest1")) +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 14),  # Adjust size for x-axis label
        axis.title.y = element_text(size = 14),  # Adjust size for y-axis label
        axis.text.x = element_text(size = 12),   # Adjust size for x-axis tick labels
        axis.text.y = element_text(size = 12)) +   # Adjust size for y-axis tick labels
  facet_wrap(~ctl_or_exper)

plot1

```

```{r}
# Plot the data with error bars
plot2b <- ggplot(summary_df, aes(x = code1, y = mean_rt, fill = code2)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(
    aes(ymin = mean_rt - se_rt, 
        ymax = mean_rt + se_rt),
    width = 0.2, 
    position = position_dodge(0.9)) +
  labs(
    x = "First Word", 
    y = "Reaction time (sec)") +
  scale_fill_manual(
    name = "Second Word", 
    labels = c("Dominant", "Irrelevant", "Nondominant"),
    values = wes_palette("GrandBudapest1")) +
  theme_minimal() +
  # geom_text(x = 1.5, y = 1.1, label = "***", size = 10, color = "black") +
  scale_x_discrete(labels = c("Dominant", "Nondominant")) +
  coord_cartesian(ylim = c(.2, .8)) + facet_grid(. ~ ctl_or_exper) 

plot2b
```


```{r}

# Add geom_text() to insert custom labels with vertical orientation
plot2b <- plot2b + geom_text(
  aes(label = custom_labels),
  position = position_dodge(width = 0.9),
  angle = 90,     # Set the angle to 90 for vertical labels
  hjust = 1.3,    # Adjust horizontal justification
  color = "white",
  size = 4
) +
  annotate("text", x = 0.5, y = .23, label = "↓", size = 7, vjust = 1)

print(plot2b)
```

```{r}
# Save the ggplot as a PNG file
# ggsave("interaction_plot_1.png", plot2b, width = 6, height = 4, dpi = 300)
```

# Mistakes model

```{r mistakes model, echo = FALSE}
DN_primes <- mistakes_included %>% filter(code1 %in% c("D", "N"))

# Filter for first choice being correct
first_choice_right <- DN_primes %>% filter(first_choice_wrong == 0)

# Helper function to create and summarize the model
run_model <- function(data, formula) {
  model <- lm(formula, data = data)
  summary(model)
}

# Models and corresponding data sets
models <- list(
  all_data = list(data = first_choice_right, formula = second_choice_wrong ~ code1 * code2),
  incong = list(data = first_choice_right %>% filter(marcel_type == "incongruent"), 
                formula = second_choice_wrong ~ code1 * ctl_or_exper),
  cong = list(data = first_choice_right %>% filter(marcel_type == "congruent"), 
              formula = second_choice_wrong ~ code1 * ctl_or_exper)
)

# Run and summarize the models
results <- map(models, ~run_model(.x$data, .x$formula))
results

```

# Mistakes plots

```{r, echo = FALSE}
second_choice_wrong$condition <- factor(second_choice_wrong$condition, levels = my_order)

dt <- table(second_choice_wrong$condition)

# Convert table to dataframe

mistakes_summary <- second_choice_wrong %>%
  filter(code1 %in% c("D", "N"), code2 %in% c("D", "N", "I")) %>%
  group_by(code1, code2) # group by columns starting with D or I

mistakes_summary <- mistakes_summary %>%
  dplyr::group_by(code1, code2, ctl_or_exper) %>%
  dplyr::summarise(Freq = n())
```

# fix from here

```{r}
# Step 1: Create a new column to represent the condition you want to calculate proportions for
filtered_columns$condition <- as.factor(filtered_columns$condition)

# Step 2: Calculate the proportions and confidence intervals separately for each value of "condition"
results <- filtered_columns %>%
  group_by(condition) %>%
  summarise(count_condition = sum(choice_2 != correct_answer_2 & choice_1 == correct_answer_1),
            count_choice_1_condition = sum(choice_1 == correct_answer_1)) %>%
  rowwise() %>%
  do({
    proportion <- .$count_condition / .$count_choice_1_condition
    ci <- binom.test(x = .$count_condition, n = .$count_choice_1_condition)$conf.int
    data.frame(., proportion = proportion, ci_lower = ci[1], ci_upper = ci[2])
  }) %>%
  ungroup()

# Add significance bars
results <- results %>%
  mutate(significance_bar = ifelse(proportion > ci_upper, "*", ifelse(proportion < ci_lower, "**", "")))

results$proportion <- results$proportion * 100
results$ci_upper <- results$ci_upper * 100
results$ci_lower <- results$ci_lower * 100

# Print the results
print(results)

# This updated code should calculate the proportions, confidence intervals, and add significance bars for count data for each condition individually.

```


```{r, echo = FALSE}
results$condition <- factor(results$condition, levels = my_order)

results <- results %>%
  separate(condition, into = c("code1", "code2"), sep = 1)

results <- results %>%
  filter(code1 %in% c("D", "N"))

add_custom_labels <- function(results) {
  results$custom_labels <- ifelse(results$code2 == "I", "irrelevant",
                                  ifelse(results$code1 == results$code2, "con.", "incongruent"))
  return(results)
}

# Assuming 'results' is your dataframe
results <- add_custom_labels(results)

# Create bar chart
mistakes_plot <- 
  ggplot(results, aes(x = code1, y = proportion, fill = code2)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "First Word", y = "% Mistakes after 1st Choice Correct") +
  scale_fill_manual(
    name = "Second Word", 
    labels = c("Dominant", "Irrelevant", "Nondominant"),
    values = wes_palette("GrandBudapest1")) +
  theme_minimal() +
  geom_errorbar(
    aes(ymin = ci_lower, ymax = ci_upper), 
    width = 0.2, 
    position = position_dodge(0.9)) +
  scale_x_discrete(labels = c("Dominant", "Nondominant")) +
  coord_cartesian(ylim = c(0, 30))

mistakes_plot

# Add geom_text() to insert custom labels with vertical orientation
mistakes_plot <- mistakes_plot + geom_text(
  aes(label = custom_labels),
  position = position_dodge(width = 0.9),
  angle = 90,     # Set the angle to 90 for vertical labels
  hjust = 1.5,    # Adjust horizontal justification
  color = "white",
  size = 4
)

print(mistakes_plot)

```

```{r}
two_by_three$code1 <- relevel(two_by_three$code1, ref = "N")
two_by_three$code2 <- relevel(two_by_three$code2, ref = "I")

# Fit the linear mixed-effects model
two_by_three_model <- lmer(on_time_2.rt ~ code1 * code2 + (1 | participant), data = two_by_three, REML = TRUE)
```
